Assessing United States county-level exposure for tropical cyclone impact research

### 2020-09-18 ehp_revision/response_to_reviewers.Rmd

---
title: "Response to reviewers' comments for *\"Assessing United States county-level exposure for research on tropical cyclones and human health\"*"
output: bookdown::pdf_document2
toc: false
bibliography: writing/hurr_exposure.bib
header-includes:
- \usepackage{xcolor}
- \usepackage{framed}
- \usepackage{bm}
- \usepackage{subcaption}
- \usepackage{gensymb}
- \renewcommand\familydefault{\sfdefault}
- \usepackage{sansmath}
- \usepackage{bm}
- \usepackage{soul}
- \sansmath
- \usepackage{booktabs}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{pdflscape}
- \usepackage{float}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fullpage}
- \usepackage{pdflscape}
- \usepackage{tcolorbox}
- \tcbuselibrary{skins,breakable}
- \usepackage{amsmath}
- \usepackage{xtab}
- \usepackage{rotating}
- \allowdisplaybreaks
- \usepackage[nomarkers]{endfloat}
- \pagenumbering{gobble}
- \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
- \usepackage{longtable}
- \DeclareDelayedFloatFlavor{longtable}{table}
- \usepackage{pdflscape}
- \setlength\LTcapwidth{\textwidth} 
---

@@

\begin{shaded}
\textbf{R1 Comment 3:}
In non-health fields, a county's inclusion in a FEMA major disaster declaration
or eligibility for public/individual assistance (all of which are somewhat
reflective of level of damage) is sometimes used as an "exposure" proxy. Have
you considered if/how your exposure assessments relate to inclusion in a FEMA
disaster declaration? In other words, does exposure to any of the hazards align
with the level of damage required for a county to be considered a "disaster
area" and/or worthy of federal assistance by current federal policy? Does this
matter?
\end{shaded}

**Response:**

This is a great question. For tropical cyclones, some health impacts will come
directly from physical exposures like wind, rain, and flooding. However, many of
the impacts might come through indirect pathways, which start from physical
hazards but move through pathways related to property damage, infrastructure
damage, access to typical medical care, mold growth, and a number of other
intermediates. Ultimately, it would be useful to have large-scale databases of
these secondary exposure pathways to use for more complex studies of the
pathways between the physical hazards of these storms and how they affect human
health. In this sense, something like the FEMA declarations could be considered
not as a proxy for assessing exposure to physical hazards, but rather as a proxy
of damage caused by the storm, and so a measurement informative for one of these
indirect pathways from physical hazards of the storm to health impacts, through
something like a mediation analysis.

However, there are some limitations to the FEMA disaster declarations in terms
of using them as a proxy for the amount of damage a storm caused in a county.
FEMA's disaster declarations are issued to provide assistance, based on damage
assessment, to individuals or the entire public in certain locations where
catastrophes overwhelm the state or local government [@mccarthy2014fema], and
any use of them for exposure assessment is secondary. Due to the political
nature of disaster declaration process, these declarations are often subject to
many political and economic factors [@mccarthy2014fema; @logue1981research].
Given the political and economic nature of these declarations, there is likely
variation across time and geography in the likelihood of a given exposure
resulting in a disaster declaration. This could be problematic for a
study that seeks to explore risk across multiple years and affected communities.

@@

\end{shaded}

**Response:**

Thank you for this suggestion, and we can see that we could have more clearly 
articulated in the original manuscript how our assessment of patterns in and 
among exposures to specific hazards can help epidemiologists to design their
studies and the statistical methods to analyze the resulting data. We provide
a detailed response in our response below to Comment 1 from this reviewer.

We have moved suggestions that the reviewer sent in "Track Changes" of the
Word document for the original manuscript and address each in detail below. When
there were several comments on a related topic, we have grouped them together to
provide a more cohesive response to the point.

@@

\begin{quotation}
\noindent
\textit{"For another set of tropical cyclones (e.g., Ernesto in 2006, and Bertha
in 1996, Isabel in 2003), there was moderate to good agreement for pairwise
combinations of distance, rain, and wind, but poor agreement for other
combinations of metrics, while for another set of storms (e.g., Matthew in 2004
and Katrina in 2005), there was moderate to good agreement between distance and
rain."}
\end{quotation}

\end{shaded}

**Response:**

We have included a measurement of agreement between different hazard-based
exposure metrics for two reasons. First, while we agree with the reviewer that a
direct measurement of each relevant hazard is preferable to a proxy, there are still some studies
that, when assessing tropical cyclone exposure based on measurements of physical
hazards, use a single hazard for this exposure assessment. We are most familar
with cases where a wind-based metric has been the focus (e.g.,
@sun2020tropical, @grabich2015measuring). While this may not be 
ideal, it is done in practice. To interpret these studies, it is helpful to
understand the degree to which this single-hazard metric agrees with exposure
patterns for other hazards. If the exposure patterns are in strong agreement for
all hazards, then these studies could be interpreted as estimating risk
associated with exposure to tropical cyclones as a whole. If the exposure
patterns are in low to moderate agreement, then these studies should be
interpreted instead as estimating the risk associated with that specific storm
hazard, but not for all storm hazards. In this case, if the agreement is
moderate, there is a chance of confounding from other storm hazards
(i.e., an association that is attributed to one storm hazard was actually the
result of another that was not included in the model). In this paper, we present
measurements of agreement across four hazard-based exposure metrics that can
provide insights on these points.

@@

If, at the county level, there were strong agreement among exposure patterns for
the different tropical cyclone hazards we considered, it might have been
reasonable to recommend the use of a single hazard-based metric as a proxy for
exposure to all storm hazards in epidemiological studies for practical reasons.
We found that this is almost never the case, although there are a few select
storms (like Hurricane Floyd in 1999) where such an approach might be
justifiable. Most atmospheric scientists would not be surprised by our findings
about this disagreement in exposure patterns for different tropical cyclone
hazards, but this finding is not as self-evident for environmental
epidemiologists. Based on a recent conference of the Interational Society for
Environmental Epidemiology, for example, there are a number of environmental
epidemiologists with backgrounds focused on methods and other ambient exposures
(e.g., air pollution, heat) who are beginning to include tropical cyclones as an
exposure of interest in their studies, and we believe these results would be
novel and useful to many of them.

Second, in cases where it is clear that a mixture approach is necessary, these
results can help in understanding what challenges might arise in statistical
analysis. While one approach to including several hazards could be to create an
index of tropical cyclone exposure by taking a weighted sum of all hazards, for
most health outcomes it is unclear *a priori* what the weight for each hazard
should be in such an index, and so it will often be preferable to discover those
weights from the data by fitting a statistical model that includes each hazard
as an independent variable. In these cases, strong correlation (or agreement, in
the case of binary exposures) among separate independent variables can create
both numerical issues (e.g., variance inflation from multicollinearity) and
difficulties in interpretation (e.g., difficulty inferring the role of specific
hazards and separating the influence of each). If an epidemiologist has a good
understanding of these patterns in the data, he or she can adopt methods that
address potential issues, including using matching-based study designs to create
a subset of storms in which separate hazards are well-distinguished,
incorporation of dimension-reduction methods like principal
components analysis, or shrinkage techniques that allow for a small amount of
bias in estimation in return for reducing problems from
collinearity (e.g., ridge regression) [@leal2012multicollinearity;
@schisterman2017collinearity].

@@

\textit{Line 514--515 from original manuscript:}

\begin{quotation}
\noindent
\textit{"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2)."}
\end{quotation}
\end{shaded}

**Response:**

This is a great suggestion. In the original manuscript, we describe this lower
correlation at higher precipitation values through the use of examples from
specific storms, and discuss the potential reasons for it. Measuring the
correlation specifically within these higher-precipitation events would add more
quantitative evidence to this discussion. We have added estimates of these
correlations specifically for high-precipitation events in a new table in the
Supplemental Material (Table S2 of the manuscript, reproduced as Table
\@ref(tab:highprecipcorr) of this response document).

@@

\input{tables/precip_high_corr.tex}

In several cases, the correlation was much weaker when limiting analysis to
these severe rainfall events. For example, in Miami-Dade County, FL, the
Spearman correlation coefficient was 0.94 for all 64 tropical cyclones that came
near the county over the analysis period, while it was only 0.49 among the 18
storms with cumulative precipitation of 75 mm or more. There was a similar
reduction in Mobile County, AL. However, for some counties, the correlation
remained high (e.g., Harris County, TX; Orleans Parish, LA), although in all
cases there are few extreme precipitation events (5--20 across
these sample counties), and so there is likely substantial random variation in
these correlation estimates, since they are based on small numbers of 
observations.

@@

We have added text to mention this point and to direct readers to the added
supplemental table:

> **Text in revised Results (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2). **Further, in some counties, the correlation was substantially lower when 
considering only tropical cyclones with cumulative local rainfall of $\ge75$ mm
(Supplemental Table 1)**."

> **Text in revised Discussion (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based observations,
but may sometimes underestimate very high rainfall values (Figure 2), **and in
some counties the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of $\ge75$ mm (Supplemental
Table 1).**"

@@

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

**Response:**

For all outcomes, there are various reasonable choices that can be picked for
the threshold in defining exposure. There is not room to go into these details
within Table 1, so instead we added a separate table to the Supplemental
Material that provides both some reasoning behind the thresholds selected in
this study and also other reasonable thresholds that could be considered.
This is Table S1 of the revised manuscript and has been reproduced as 
Table \@ref(tab:thresholds) at the end of this response document.

\begin{longtable}{lp{35em}}
\caption{Reasons behind the choices of thresholds for binary exposure classifications, as well as discussion of some other reasonable choices. These are provided for the three exposure metrics for which our database includes continuous data, and so a threshold is selected to determine binary exposure based on the metric. This table provides reasoning for the choice of threshold used in this paper as well as guidance on other thresholds that could be considered, depending on the hypothesized pathways for an epidemiological study.} \\
\label{tab:thresholds} \\
\hline
Metric & Threshold choice\\
\hline
\textbf{Distance} & Distance-based exposure was determined based on whether the storm track came within 100 km of county population mean center. This threshold has been used in prior research as a proxy for exposure to hazards from the storm (e.g., @grabich2015measuring). Tropical cyclones vary dramatically in size: US tropical cyclones have been observed with radii to maximum winds as small as 20 km and as large as 200 km [@mallin2006; @quiring2011variations], and dangerous winds can extend beyond these maximum winds. One study assessed county-level risk and exposure based on a three-tiered definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary counties, and tertiary counties adjacent to secondary counties, which resulted in an average distance radius of 120 km on either side of the storm track [@czajkowski2011]. Other distance thresholds that could be considered include 60 km and 30 km, both of which have been used in previous research [@grabich2015measuring; @grabich2015; @currie2013]. However, based on the results presented in the main manuscript, hazard-based metrics should often be used directly rather than a distance-based proxy.\\

\textbf{Rain} & Rain-based exposure was determined based on whether the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. One recent study has highlighted that a two-year rainfall value (which is the median annual maximum rainfall) for a location can provide a useful threshold in identifying rainfall events with potential for societal impacts [@bosma2020intuitive]. For some of the more northern, inland communities included in our study area, the two-year rainfall value for two-, three- and four-day windows is in the 65--85 mm range. For example, Pittsburgh, PA, has two-year rainfall values of 69 mm for a two-day window, 74 mm for a three-day window, and 78 mm for a four-day window [@noaaatlas], consistent with the 75 mm threshold we selected for exposure classification in this paper. However, other thresholds, particularly higher thresholds, would be reasonable in some cases. For example, the two-year rainfall values tend to be much higher in counties of the study area that are further south and close to the coast. The two-year rainfall value for Miami for a three-day window, for example is 180 mm [@noaaatlas]. A variety of definitions have been used previously to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall [@zhou2017spatial] and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---\parfillskip=0pt\tabularnewline

&in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location [@feldmann2019estimation]. Other definitions of extreme rain events---including but not limited to tropical cyclone--associated rainfall---are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours [@schumacher2006characteristics]. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]). [@schumacher2006characteristics; @schumacher2005organization; @stevenson201410].\\

\textbf{Wind} & Wind-based exposure was determined based on whether modeled storm-associated peak sustained surface wind were $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts [@cangialosi2016examination]. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

### 2020-09-18 ehp_revision/tables/flood_misclass.tex
Work some more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\label{tab:misclassflood}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and flood metric & Exposed for distance metric but unexposed for flood metric & Exposed for flood metric but unexposed for distance metric & Unexposed for both distance metric and flood metric \\ 
  \midrule
Ivan (2004) & 79 & 205 & 238 & 1,874 \\ 
  Frances (2004) & 103 & 218 & 122 & 1,953 \\ 
  Dennis (2005) & 21 & 271 & 87 & 2,017 \\ 
  Jeanne (2004) & 80 & 217 & 77 & 2,022 \\ 
  Allison (2001) & 68 & 219 & 71 & 2,038 \\ 
  Cindy (2005) & 52 & 269 & 29 & 2,046 \\ 
  Ike (2008) & 48 & 185 & 101 & 2,062 \\ 
  Isidore (2002) & 30 & 238 & 64 & 2,064 \\ 
  Fay (2008) & 23 & 229 & 60 & 2,084 \\ 
  Bill (2003) & 39 & 191 & 65 & 2,101 \\ 
  Gustav (2008) & 36 & 198 & 57 & 2,105 \\ 
  Katrina (2005) & 47 & 194 & 47 & 2,108 \\ 
  Gordon (2000) & 7 & 248 & 19 & 2,122 \\ 
  Arlene (2005) & 11 & 225 & 29 & 2,131 \\ 
  Danny (1997) & 39 & 190 & 31 & 2,136 \\ 
  Floyd (1999) & 100 & 39 & 120 & 2,137 \\ 
  Fran (1996) & 46 & 105 & 77 & 2,168 \\ 
  Dennis (1999) & 38 & 162 & 19 & 2,177 \\ 
  Ernesto (2006) & 44 & 148 & 27 & 2,177 \\ 
  Hanna (2008) & 52 & 140 & 26 & 2,178 \\ 
  Helene (2000) & 13 & 179 & 20 & 2,184 \\ 
  Bertha (1996) & 27 & 156 & 17 & 2,196 \\ 
  Irene (2011) & 108 & 12 & 79 & 2,197 \\ 
  Rita (2005) & 4 & 161 & 26 & 2,205 \\ 
  Earl (1998) & 4 & 165 & 11 & 2,216 \\ 
  Lee (2011) & 18 & 126 & 36 & 2,216 \\ 
  Hermine (2010) & 16 & 107 & 40 & 2,233 \\ 
  Isabel (2003) & 39 & 108 & 9 & 2,240 \\ 
  Josephine (1996) & 27 & 96 & 32 & 2,241 \\ 
  Bonnie (2004) & 10 & 99 & 29 & 2,258 \\ 
  Frances (1998) & 8 & 54 & 23 & 2,311 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Fri Sep 18 10:32:13 2020
\begin{table}[ht]
\centering
\caption{Agreement between flood-based exposure assessment and a distance-based
         proxy of storm exposure for tropical cyclones with at least 200 counties assessed 
         as exposed based on at least one exposure metric considered in this study. Numbers 
         are out of 2,396 counties in the study area (states in the eastern half of the US; 
         Figure 1 of the main text). Exposure assessment is based on the thresholds given in 
         Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is 
         calculated as the value in the second column divided by the sum of numbers in the 
         second through fourth columns.  Storms are ordered based on the number of counties 
         assessed as exposed to at least one of these two exposure metrics.).} 
\label{tab:misclassflood}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and flood metric & Exposed for distance metric but unexposed for flood metric & Exposed for flood metric but unexposed for distance metric & Unexposed for both distance metric and flood metric \\ 
  \midrule
Ivan (2004) & 79 & 205 & 238 & 1,874 \\ 
  Frances (2004) & 103 & 218 & 122 & 1,953 \\ 
  Dennis (2005) & 21 & 271 & 87 & 2,017 \\ 
  Jeanne (2004) & 80 & 217 & 77 & 2,022 \\ 
  Allison (2001) & 68 & 219 & 71 & 2,038 \\ 
  Cindy (2005) & 52 & 269 & 29 & 2,046 \\ 
  Ike (2008) & 48 & 185 & 101 & 2,062 \\ 
  Isidore (2002) & 30 & 238 & 64 & 2,064 \\ 
  Fay (2008) & 23 & 229 & 60 & 2,084 \\ 
  Bill (2003) & 39 & 191 & 65 & 2,101 \\ 
  Gustav (2008) & 36 & 198 & 57 & 2,105 \\ 
  Katrina (2005) & 47 & 194 & 47 & 2,108 \\ 
  Gordon (2000) & 7 & 248 & 19 & 2,122 \\ 
  Arlene (2005) & 11 & 225 & 29 & 2,131 \\ 
  Danny (1997) & 39 & 190 & 31 & 2,136 \\ 
  Floyd (1999) & 100 & 39 & 120 & 2,137 \\ 
  Fran (1996) & 46 & 105 & 77 & 2,168 \\ 
  Dennis (1999) & 38 & 162 & 19 & 2,177 \\ 
  Ernesto (2006) & 44 & 148 & 27 & 2,177 \\ 
  Hanna (2008) & 52 & 140 & 26 & 2,178 \\ 
  Helene (2000) & 13 & 179 & 20 & 2,184 \\ 
  Bertha (1996) & 27 & 156 & 17 & 2,196 \\ 
  Irene (2011) & 108 & 12 & 79 & 2,197 \\ 
  Rita (2005) & 4 & 161 & 26 & 2,205 \\ 
  Earl (1998) & 4 & 165 & 11 & 2,216 \\ 
  Lee (2011) & 18 & 126 & 36 & 2,216 \\ 
  Hermine (2010) & 16 & 107 & 40 & 2,233 \\ 
  Isabel (2003) & 39 & 108 & 9 & 2,240 \\ 
  Josephine (1996) & 27 & 96 & 32 & 2,241 \\ 
  Bonnie (2004) & 10 & 99 & 29 & 2,258 \\ 
  Frances (1998) & 8 & 54 & 23 & 2,311 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-18 ehp_revision/tables/rain_misclass.tex
Work some more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns.  Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.).} 
\label{tab:misclassrain}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and rain metric & Exposed for distance metric but unexposed for rain metric & Exposed for rain metric but unexposed for distance metric & Unexposed for both distance metric and rain metric \\ 
  \midrule
Frances (2004) & 207 & 114 & 257 & 1,818 \\ 
  Ivan (2004) & 124 & 160 & 288 & 1,824 \\ 
  Isidore (2002) & 134 & 134 & 186 & 1,942 \\ 
  Ike (2008) & 113 & 120 & 213 & 1,950 \\ 
  Dennis (2005) & 48 & 244 & 124 & 1,980 \\ 
  Fay (2008) & 72 & 180 & 163 & 1,981 \\ 
  Jeanne (2004) & 144 & 153 & 113 & 1,986 \\ 
  Lee (2011) & 106 & 38 & 230 & 2,022 \\ 
  Gustav (2008) & 126 & 108 & 137 & 2,025 \\ 
  Allison (2001) & 106 & 181 & 67 & 2,042 \\ 
  Bill (2003) & 110 & 120 & 117 & 2,049 \\ 
  Cindy (2005) & 78 & 243 & 11 & 2,064 \\ 
  Floyd (1999) & 129 & 10 & 170 & 2,087 \\ 
  Katrina (2005) & 195 & 46 & 58 & 2,097 \\ 
  Danny (1997) & 82 & 147 & 54 & 2,113 \\ 
  Rita (2005) & 64 & 101 & 103 & 2,128 \\ 
  Gordon (2000) & 5 & 250 & 7 & 2,134 \\ 
  Arlene (2005) & 39 & 197 & 23 & 2,137 \\ 
  Dennis (1999) & 90 & 110 & 56 & 2,140 \\ 
  Ernesto (2006) & 124 & 68 & 63 & 2,141 \\ 
  Irene (2011) & 119 & 1 & 106 & 2,170 \\ 
  Hanna (2008) & 100 & 92 & 33 & 2,171 \\ 
  Hermine (2010) & 44 & 79 & 102 & 2,171 \\ 
  Fran (1996) & 89 & 62 & 73 & 2,172 \\ 
  Earl (1998) & 72 & 97 & 38 & 2,189 \\ 
  Bertha (1996) & 103 & 80 & 20 & 2,193 \\ 
  Helene (2000) & 28 & 164 & 11 & 2,193 \\ 
  Frances (1998) & 27 & 35 & 139 & 2,195 \\ 
  Josephine (1996) & 94 & 29 & 77 & 2,196 \\ 
  Bonnie (2004) & 56 & 53 & 56 & 2,231 \\ 
  Isabel (2003) & 88 & 59 & 17 & 2,232 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Fri Sep 18 10:32:05 2020
\begin{table}[ht]
\centering
\caption{Agreement between rain-based exposure assessment and a distance-based
         proxy of storm exposure for tropical cyclones with at least 200 counties assessed 
         as exposed based on at least one exposure metric considered in this study. Numbers 
         are out of 2,396 counties in the study area (states in the eastern half of the US; 
         Figure 1 of the main text). Exposure assessment is based on the thresholds given in 
         Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is 
         calculated as the value in the second column divided by the sum of numbers in the 
         second through fourth columns.  Storms are ordered based on the number of counties 
         assessed as exposed to at least one of these two exposure metrics.).} 
\label{tab:misclassrain}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and rain metric & Exposed for distance metric but unexposed for rain metric & Exposed for rain metric but unexposed for distance metric & Unexposed for both distance metric and rain metric \\ 
  \midrule
Frances (2004) & 207 & 114 & 257 & 1,818 \\ 
  Ivan (2004) & 124 & 160 & 288 & 1,824 \\ 
  Isidore (2002) & 134 & 134 & 186 & 1,942 \\ 
  Ike (2008) & 113 & 120 & 213 & 1,950 \\ 
  Dennis (2005) & 48 & 244 & 124 & 1,980 \\ 
  Fay (2008) & 72 & 180 & 163 & 1,981 \\ 
  Jeanne (2004) & 144 & 153 & 113 & 1,986 \\ 
  Lee (2011) & 106 & 38 & 230 & 2,022 \\ 
  Gustav (2008) & 126 & 108 & 137 & 2,025 \\ 
  Allison (2001) & 106 & 181 & 67 & 2,042 \\ 
  Bill (2003) & 110 & 120 & 117 & 2,049 \\ 
  Cindy (2005) & 78 & 243 & 11 & 2,064 \\ 
  Floyd (1999) & 129 & 10 & 170 & 2,087 \\ 
  Katrina (2005) & 195 & 46 & 58 & 2,097 \\ 
  Danny (1997) & 82 & 147 & 54 & 2,113 \\ 
  Rita (2005) & 64 & 101 & 103 & 2,128 \\ 
  Gordon (2000) & 5 & 250 & 7 & 2,134 \\ 
  Arlene (2005) & 39 & 197 & 23 & 2,137 \\ 
  Dennis (1999) & 90 & 110 & 56 & 2,140 \\ 
  Ernesto (2006) & 124 & 68 & 63 & 2,141 \\ 
  Irene (2011) & 119 & 1 & 106 & 2,170 \\ 
  Hanna (2008) & 100 & 92 & 33 & 2,171 \\ 
  Hermine (2010) & 44 & 79 & 102 & 2,171 \\ 
  Fran (1996) & 89 & 62 & 73 & 2,172 \\ 
  Earl (1998) & 72 & 97 & 38 & 2,189 \\ 
  Bertha (1996) & 103 & 80 & 20 & 2,193 \\ 
  Helene (2000) & 28 & 164 & 11 & 2,193 \\ 
  Frances (1998) & 27 & 35 & 139 & 2,195 \\ 
  Josephine (1996) & 94 & 29 & 77 & 2,196 \\ 
  Bonnie (2004) & 56 & 53 & 56 & 2,231 \\ 
  Isabel (2003) & 88 & 59 & 17 & 2,232 \\ 
   \bottomrule
\end{tabular}
\end{table}
